\LARGE \bfseries \vspace{-2cm} Burden and health-related quality of life among caregivers of people with motor neuron disease

### 2024-06-15 output/manuscript.tex
Updates from Overleaf

\hspace{1em}
\begin{table}[H]
    \centering \singlespacing \small
    \caption{Categorization of independent variables}
    \begin{tabular}{|L{6cm}|L{9cm}|}
        \hline
        \PlainInput{tables/tab_var_category}
    \end{tabular}
    \label{tab_var_category}
    \caption*{\footnotesize \textit{Notes:} Donec sit amet viverra justo}
\end{table}

@@

\hspace{1em}
\begin{table}[H]
    \centering \singlespacing \small
    \caption{Patients’ and caregivers characteristics, patients' functional status (ALSFRS-R), caregiver burden (ZBI score), and caregiver health-related quality of life (EQ-5D) at baseline}
    \begin{tabular}{|L{5cm}|R{3.2cm}|}
        \hline
        \PlainInput{tables/tab_desc_stat}
    \end{tabular}
    \label{tab_desc_stat}
    \caption*{\footnotesize \textit{Notes:} Data are based on participants with non-missing baseline caregiver burden and quality of life data. ALSFRS-R, Revised Amyotrophic Lateral Sclerosis Functional Rating Scale; EQ-5D, EuroQol 5-dimension questionnaire; n, number; SD, standard deviation, VAS, visual analog scale; ZBI, Zarit Burden Interview.
}
\end{table}

@@

\hspace{1em}
\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]{figures/outcome-kings-stage.png}
    \caption{EQ-5D-5L utility scores, domain scores and scores by King’s stage}
    \label{fig:outcome-kings-stage}
    \caption*{\footnotesize \textit{Notes:} ANOVA, analysis of variance; EQ-5D, EuroQol 5-dimension questionnaire; VAS, visual analog scale; ZBI, Zarit Burden Interview}
\end{figure}

\hspace{1em}
\begin{table}[H]
    \centering \singlespacing \small
    \caption{Pooled carer ZBI, EQ-VAS, and EQ-5D utility and domain scores by King’s stage}
    \begin{tabular}{|L{.33\linewidth}|R{.1\linewidth}|R{.1\linewidth}|R{.1\linewidth}|R{.1\linewidth}|R{.1\linewidth}|}
        \hline
        \PlainInput{tables/tab_outcomes_kings}
    \end{tabular}
    \label{tab_outcomes_kings}
    \caption*{\footnotesize 
                \textit{Notes:} Data from all caregivers at all time points (baseline, 6 months, and 9 months) have been pooled. Comparisons of outcomes between King’s stages use ANOVA. ZBI total score ranges from 0 to 88, with higher scores indicating greater burden. EQ-5D scores range from 0 to 1.0, with higher scores indicating better health-related quality of life. EQ-VAS scores range from 0 to 100, with higher scores indicate better health-related quality of life. EQ-5D domain scores range from 0 to 3, with higher scores indicating greater restriction by domain. \\
                ANOVA, analysis of variance; EQ-5D, EuroQol 5-dimension questionnaire; VAS, visual analog scale; ZBI, Zarit Burden Interview}
\end{table}

\subsection{Caregiver HRQoL and burden over time}
The mean (SD) change in carers ZBI scores from baseline to 18 months was X.X (X.X) for the caregiver EQ-5D index score,X.X (X.X) for the caregiver EQ-5D VAS score, and X.X (X.X) for the ZBI score. For the two HRQoL measures, the change from baseline to 6 months or 9 months was not significant. We found significant differences in ZBI scores between 0 and 9  months (p value = X.XXX), mostly driven by the change ins cores beuween 0 and 6 months. \autoref{fig:eq5d-scores-time} shows the EQ-5D domain scores over time. At baseline, no caregiver had any problem in self-care domain. %Examination of the EQ-5D domain scores (Fig. 1) showed that very few caregivers had extreme problems (<5\% for any domain) and the levels of problems were similar at baseline and at 18 months. At both time points, more caregivers had some problems in the domains of pain/discomfort (baseline: 42.8\%; 18 months: 46.8\%) and anxiety/depression (baseline: 30.3\%; 18 months: 33.9\%) than in the other three domains.

\hspace{1em}
\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]{figures/eq5d-scores-time.png}
    \caption{Problems in the caregiver EQ-5D domains at baseline, 6 months, and 9 months.}
    \label{fig:eq5d-scores-time}
    \caption*{\footnotesize \textit{Notes:} ANOVA, analysis of variance; EQ-5D, EuroQol 5-dimension questionnaire; VAS, visual analog scale; ZBI, Zarit Burden Interview}
\end{figure}

>>>>

\begin{table}[H]
    \centering \singlespacing \small
    \caption{Categorization of independent variables}
    \begin{tabular}{|L{6cm}|L{9cm}|}
        \hline
        \PlainInput{tables/tab_var_category}
    \end{tabular}
    \label{tab_var_category}
    \caption*{\footnotesize \textit{Notes:} Donec sit amet viverra justo}
\end{table}

@@

\begin{table}[H]
    \centering \singlespacing \small
    \caption{Patients’ and caregivers characteristics, patients' functional status (ALSFRS-R), caregiver burden (ZBI score), and caregiver health-related quality of life (EQ-5D) at baseline}
    \begin{tabular}{|L{5cm}|R{3.2cm}|}
        \hline
        \PlainInput{tables/tab_desc_stat}
    \end{tabular}
    \label{tab_desc_stat}
    \caption*{\footnotesize \textit{Notes:} Data are based on participants with non-missing baseline caregiver burden and quality of life data. ALSFRS-R, Revised Amyotrophic Lateral Sclerosis Functional Rating Scale; EQ-5D, EuroQol 5-dimension questionnaire; n, number; SD, standard deviation, VAS, visual analog scale; ZBI, Zarit Burden Interview.
}
\end{table}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]{figures/outcome-kings-stage.png}
    \caption{EQ-5D-5L utility scores, domain scores and scores by King’s stage}
    \label{fig:outcome-kings-stage}
    \caption*{\footnotesize \textit{Notes:} ANOVA, analysis of variance; EQ-5D, EuroQol 5-dimension questionnaire; VAS, visual analog scale; ZBI, Zarit Burden Interview}
\end{figure}

\begin{table}[H]
    \centering \singlespacing \small
    \caption{Pooled carer ZBI, EQ-VAS, and EQ-5D utility and domain scores by King’s stage}
    \begin{tabular}{|L{.33\linewidth}|R{.1\linewidth}|R{.1\linewidth}|R{.1\linewidth}|R{.1\linewidth}|R{.1\linewidth}|}
        \hline
        \PlainInput{tables/tab_outcomes_kings}
    \end{tabular}
    \label{tab_outcomes_kings}
    \caption*{\footnotesize 
                \textit{Notes:} Data from all caregivers at all time points (baseline, 6 months, and 9 months) have been pooled. Comparisons of outcomes between King’s stages use ANOVA. ZBI total score ranges from 0 to 88, with higher scores indicating greater burden. EQ-5D scores range from 0 to 1.0, with higher scores indicating better health-related quality of life. EQ-VAS scores range from 0 to 100, with higher scores indicate better health-related quality of life. EQ-5D domain scores range from 0 to 3, with higher scores indicating greater restriction by domain. \\
                ANOVA, analysis of variance; EQ-5D, EuroQol 5-dimension questionnaire; VAS, visual analog scale; ZBI, Zarit Burden Interview}
\end{table}

\subsection{Caregiver HRQoL and burden over time}
The mean (SD) change in carers ZBI scores from baseline to 18 months was X.X (X.X) for the caregiver EQ-5D index score,X.X (X.X) for the caregiver EQ-5D VAS score, and X.X (X.X) for the ZBI score. For the two HRQoL measures, the change from baseline to 6 months or 9 months was not significant. We found significant differences in ZBI scores between 0 and 9  months (p value = X.XXX), mostly driven by the change ins cores beuween 0 and 6 months.

\autoref{fig:eq5d-scores-time} shows the EQ-5D domain scores over time. At baseline, no caregiver had any problem in self-care domain. %Examination of the EQ-5D domain scores (Fig. 1) showed that very few caregivers had extreme problems (<5\% for any domain) and the levels of problems were similar at baseline and at 18 months. At both time points, more caregivers had some problems in the domains of pain/discomfort (baseline: 42.8\%; 18 months: 46.8\%) and anxiety/depression (baseline: 30.3\%; 18 months: 33.9\%) than in the other three domains.

\begin{table}[H]
    \centering \singlespacing \small
    \caption{Means differences (95\% confidence intervals) and p-values from t-tests comparing of caregiver ZBI, EQ-VAS, and EQ-5D scores changes over time}
    \begin{tabular}{|L{6cm}|C{5cm}|C{2.5cm}|}
        \hline
        \PlainInput{tables/outcome-scores-time}
    \end{tabular}
    \label{outcome-scores-time}
    \caption*{\footnotesize 
                \textit{Notes:} CI, confidence interval; EQ-5D, EuroQol 5-dimension questionnaire; VAS, visual analog scale; ZBI, Zarit Burden Interview}
\end{table}

\hspace{1em}
\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]{figures/eq5d-domains-time.png}
    \caption{Problems in the caregiver EQ-5D domains at baseline, 6 months, and 9 months.}
    \label{fig:eq5d-scores-time}
    \caption*{\footnotesize \textit{Notes:} ANOVA, analysis of variance; EQ-5D, EuroQol 5-dimension questionnaire; VAS, visual analog scale; ZBI, Zarit Burden Interview}
\end{figure}
